### 2013-11-24 PositionPaper/incremental.tex
Stabilizing section 3 ... a less abstract idea on how to deal with agreed and global SLA

This first stage of our data integration and provision process is  defined as a vertical mapping of SLAs that are expressed as macroscopic constraints: execution time, pay / no pay, data reliability, data source. The system should be able to find relevant service compositions that respond to the query  such that when combined, meet the constraints imposed by the user (High level SLA). One may think to a first filter to remove the individual services which do not meet some or all of the constraints expressed by the user.

To meet this objective, we assume that services export SLA's (agreed SLA's) that are sometimes of finer granularity than those defined by the user. So the challenge  is  to determine whether their joint use is compatible with the individual SLA. This step may lead either to the rejection of integration in case of total incompatibility, or to a negotiation between SLA which will lead us to the proposal for a negotiated SLA integration and thus the need for an adaptive setting.

 \begin{enumerate}
\item Computation of a global SLA given the existing possible SLA agreed by data providers that can be called for answering the query. Data providers are filtered in this way, since only those agreed SLA that can be combined into a global SLA that can fulfill the user preferences are considered for retrieving data.

  \item Filter the data providers that can potentially participate in the evaluation of the query taking into consideration the preferences associated to the query.

  \item Negociation of this type of SLA depends strongly on the request sent and the services deployed at the arrival time of the application on the cloud. This negotiation can be expensive and may not scale well.
  \end{enumerate}

%-----------------------------------------------------------------
\subsection{Query Rewriting}
\label{sec:queryRew}
%-----------------------------------------------------------------
{\color{red}
See wether a similar Q has been already rewritten or rewrite it. Executing a query requires first a semantic analysis which will subdivide R into a set of sub-queries, in such a way that each sub-query can be processed by a DataService deployed on the cloud.   The subqueries represent the possible combination of services that can answer the initial query with given SLA.
}

>>>>

This first stage of our data integration and provision process is  defined as a vertical mapping of SLAs that are expressed as macroscopic constraints (i.e., high level SLA): execution time, pay / no pay, data reliability, data source. The system  finds relevant service compositions that respond to the query  such that when combined, they meet the constraints imposed by the user. One may think to a first filter to remove the individual services which do not meet some or all of the constraints expressed by the user.

To meet this objective, we assume that services export SLA's (i.e., agreed SLA's) that are sometimes of finer granularity than those defined by the user.  The service SLA measures are are: response time, availability, price/call, reliability, data production rate. Other measures are associated to the conditions in which the service is called. For example the cost, which includes the price of calling the service, plus the price of data transmision according to the amount of trasnmitted MegaOctets through the network and the type of subscription of the user for using the network. With this measures the service has an associated agreed SLA expressed through a XML document using the specification WSLA (Web service level agreement \footnote{http://www.research.ibm.com/people/a/akeller/Data/WSLASpecV1-20030128.pdf}).
Since we assume that services can be deployed on different cloud providers, measures and SLA threasholds can vary.

The challenge  is  to determine whether their joint use is compatible with the individual SLA. This step may lead either to the rejection of integration in case of total incompatibility, or to a negotiation between SLA which will lead us to the proposal for a negotiated SLA integration and thus the need for an adaptive setting.

% \begin{enumerate}
%\item Computation of a global SLA given the existing possible SLA agreed by data providers that can be called for answering the query. Data providers are filtered in this way, since only those agreed SLA that can be combined into a global SLA that can fulfill the user preferences are considered for retrieving data.

%  \item Filter the data providers that can potentially participate in the evaluation of the query taking into consideration the preferences associated to the query.

 % \item 
 Negociation of this type of SLA depends strongly on the request sent and the services deployed at the arrival time of the application on the cloud. This negotiation can be expensive and may not scale well.
 % \end{enumerate}

%-----------------------------------------------------------------
\subsection{Query Rewriting}
\label{sec:queryRew}
%-----------------------------------------------------------------
%{\color{red}
%See wether a similar Q has been already rewritten or rewrite it. Executing a query requires first a semantic analysis which will subdivide R into a set of sub-queries, in such a way that each sub-query can be processed by a DataService deployed on the cloud.   The subqueries represent the possible combination of services that can answer the initial query with given SLA.
%}
